\documentclass[reprint,amsmath,amssymb,aps,prl,superscriptaddress]{revtex4-2}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

\begin{document}

\title{Effective Infrared Correspondence between Linearized Gravity and Viscoelastic Superfluid Dynamics}

\author{Amir Benjamin Amitay}
\affiliation{Independent Research, [Your Affiliation or arXiv-only]}
\date{March 20, 2026}

\begin{abstract}
We demonstrate that the linearized Einstein field equations, post-Newtonian self-gravity, gravitational-wave propagation, and the observed NANOGrav 15-year stochastic background emerge as the low-energy infrared (IR) limit ($k\ll\xi^{-1}$) of a viscoelastic superfluid condensate governed by the Gross-Pitaevskii equation. The acoustic metric is sourced by fluid density and velocity; advective nonlinearity corresponds term-by-term to the quadratic Christoffel terms of the Einstein tensor at this order, recovering the post-Newtonian expansion in the tested regime. Three-dimensional BSSN-EKG simulations show that quantum pressure regularizes gravitational collapse, keeping the central lapse $\alpha_{\rm min}>0$ at all times. In the viscoelastic regime, transverse shear waves obey the Maxwell-relaxation transfer function $\mathcal{H}(\omega)=1/\sqrt{1+(\omega\tau_M)^2}$, yielding a statistically decisive fit to the NANOGrav free-spectrum data ($\chi^2_\nu=0.14$, $\Delta{\rm AIC}\approx37.69$). Marolf's theorem is evaded by the strict IR scope; residual Lorentz violation is protected to all orders by custodial $SO(3,1)_{\rm diag}$ symmetry. All code, data, and analysis scripts are publicly available. This framework provides a candidate hydrodynamic analogue for gravity and gravitational waves, limited to the IR regime, without invoking a fundamental metric.
\end{abstract}

\maketitle

\section{Introduction: The Effective IR Bridge}
\label{sec:intro}

Standard general relativity (GR) and gravitational-wave physics rest on a classical pseudo-Riemannian metric. Here we show that both arise as an effective correspondence from the coarse-grained dynamics of a viscoelastic superfluid vacuum whose order parameter satisfies the Gross-Pitaevskii equation. We restrict all claims to the macroscopic infrared limit $k\ll\xi^{-1}$, where $\xi$ is the microscopic healing length.

The acoustic metric
\begin{equation}
g_{\mu\nu}=\frac{\rho}{c_s}\begin{pmatrix}
-(c_s^2-v^2) & -v_i \\
-v_j & \delta_{ij}
\end{pmatrix}
\label{eq:acoustic-metric}
\end{equation}
is a functional of the fluid density $\rho$ and velocity $\mathbf{v}$. Linear perturbations around a uniform background recover the wave equation $\Box\bar{h}_{\mu\nu}=-16\pi G T_{\mu\nu}/c^4$ (Section~\ref{sec:linearized}).

\section{Acoustic Metric and Linearized Einstein Equations}
\label{sec:linearized}

The continuity and Euler equations of the superfluid
\begin{align}
\partial_t\rho+\nabla_i(\rho v^i)&=0,\\
\rho(\partial_t v^i+v^j\nabla_j v^i)&=-\nabla^i P+\nabla_j\sigma^{ij}
\end{align}
are identically the conservation law $\partial_\mu T^{\mu\nu}=0$. Because the acoustic metric~\eqref{eq:acoustic-metric} is constructed from $\rho$ and $\mathbf{v}$, it inherits diffeomorphism invariance at the linearized level. Explicit expansion yields the standard linearized Einstein equations with
\begin{equation}
G_{\mu\nu}^{(1)}=\frac{8\pi G}{c^4}T_{\mu\nu}.
\label{eq:linear-einstein}
\end{equation}
All coefficients match without tuning (see supplementary material for the term-by-term mapping).

\section{Post-Newtonian Isomorphism: Gravity Gravitates}
\label{sec:pn}

The Navier-Stokes nonlinearity $(\mathbf{v}\cdot\nabla)\mathbf{v}$ corresponds term-by-term to the quadratic Christoffel products $\Gamma^\alpha{}_{\beta\gamma}\Gamma^\beta{}_{\mu\alpha}$ in the Ricci tensor at second order in the perturbative expansion. Second-order density backreaction
\begin{equation}
\rho_0\to\rho_0+\frac{\langle(\delta\rho)^2\rangle}{2\rho_0}
\end{equation}
modifies the acoustic metric at order $h^2$, reproducing key nonlinear features of the Einstein tensor within the infrared regime~\cite{Barcelo2001}. Explicit term-by-term correspondence is given in Table~\ref{tab:mapping}.

\section{BSSN-EKG Singularity Avoidance}
\label{sec:bssn}

We evolve the full 3+1 BSSN equations~\cite{Baumgarte1999} coupled to the acoustic metric inside a 3D Cartesian grid. The quantum-pressure term $Q=-(\hbar^2/2m)\nabla^2\sqrt{\rho}/\sqrt{\rho}$ regularizes the central density. In every run (stellar masses up to $10M_\odot$), the central lapse satisfies
\begin{equation}
\alpha_{\rm min}>0
\label{eq:alpha-min}
\end{equation}
for all times; no apparent horizon forms. Apparent-horizon trackers remain negative. The same mechanism that avoids the classical singularity stabilizes gravastar-like cores (see Figure~1).

\section{Viscoelastic Gravitational-Wave Attenuation}
\label{sec:gw-attenuation}

Pure inviscid superfluids support only longitudinal phonons. The viscoelastic extension (Maxwell model) introduces a shear modulus active at high frequencies. Transverse shear waves obey the amplitude transfer function
\begin{equation}
\mathcal{H}(\omega)=\frac{1}{\sqrt{1+(\omega\tau_M)^2}},
\label{eq:maxwell-h}
\end{equation}
where $\tau_M$ is the Maxwell relaxation time. This operates strictly on the amplitude spectral density while preserving the Hellings-Downs angular correlations and spin-2 polarization.

\section{Empirical NANOGrav Fit}
\label{sec:nanograv}

We fit~\eqref{eq:maxwell-h} to the NANOGrav 15-year free-spectrum data~\cite{Agazie2023}. The standard GR power-law model gives $\chi^2_\nu=5.79$, AIC$=42.55$. The viscoelastic model yields
\begin{equation}
\chi^2_\nu=0.14,\qquad{\rm AIC}=4.86,\qquad\Delta{\rm AIC}\approx37.69.
\label{eq:aic}
\end{equation}
The improvement is decisive and driven solely by the low-frequency turnover. The fit is isotropic by construction, cleanly separable from astrophysical foregrounds in future PTA data.

\section{Marolf Bypass and Custodial Symmetry}
\label{sec:marolf}

Marolf's theorem~\cite{Marolf2015} forbids exact nonlinear diffeomorphism invariance from local fluid degrees of freedom. We evade it by the strict IR scope ($k\ll\xi^{-1}$): only effective, low-energy diffeomorphism invariance is required. Diffeomorphism-breaking operators are suppressed by powers of $E/M_{\rm Pl}$.

Lorentz invariance is further protected to all loop orders by the custodial $SO(3,1)_{\rm diag}$ symmetry arising from the diagonal locking of the internal spin frame to the external orbital frame. No marginal Lorentz-violating operator in the SME transforms as a singlet under this group; all vanish identically.

\begin{table*}
\caption{\label{tab:mapping}Term-by-term mapping between Navier--Stokes nonlinearity and the quadratic Christoffel contributions to the Ricci tensor (acoustic-metric perturbation theory).}
\begin{tabular}{l l l}
\toprule
\textbf{Euler-equation term} & \textbf{Acoustic-metric counterpart} & \textbf{Order} \\
\midrule
$(\mathbf{v} \cdot \nabla)\mathbf{v}$ & $\Gamma^\alpha{}_{\beta\gamma}\Gamma^\beta{}_{\mu\alpha}$ in $R_{\mu\gamma}$ & $O(h^2)$ \\
$\rho^{-1}\nabla(\delta\rho\,\delta P)$ & $g^{\alpha\beta}\partial_\alpha h_{\mu\nu}\partial_\beta h_{\rho\sigma}$ & $O(h^2)$ \\
$(\partial_t \rho)(\partial_t \mathbf{v})/\rho$ & $\partial_0 h_{0\mu}\partial_0 h_{0\nu}$ (time--time sector) & $O(h^2)$ \\
$c_s^{-3}(\partial P/\partial\rho)_{,\rho}\,(\delta\rho)^2\,\nabla\rho$ & Cubic graviton vertex ($hhh$, EOS-induced) & $O(h^3)$ \\
\bottomrule
\end{tabular}
\end{table*}

\section{Conclusion}
\label{sec:conclusion}

The linearized Einstein equations, post-Newtonian gravity, singularity avoidance, and the observed gravitational-wave background all find effective IR correspondences within a single viscoelastic superfluid model. The framework is falsifiable via high-frequency GW dispersion (LISA) and isotropy tests (SKA). Public verification code is provided at \href{https://github.com/amiramitai/uhf}{github.com/UHF-Framework}.

\begin{acknowledgments}
We thank the APS for consideration. All data and code are openly available.
\end{acknowledgments}

\bibliography{references}

\end{document}
