\documentclass[reprint,amsmath,amssymb,aps,prl,superscriptaddress]{revtex4-2}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

\begin{document}

\title{Heuristic Superfluid Cosmology: Collapse-Threshold Estimates for Early-Galaxy Abundance and a Topological Analogue of Collisionless Dark Matter}

\author{Amir Benjamin Amitay}
\affiliation{Independent Research}

\date{March 21, 2026}

\begin{abstract}
We explore a heuristic cosmological scenario in which the dark sector is modeled as a viscoelastic superfluid condensate whose inertial mass obeys $m=C\rho_0V$ ($C=3.523\pm0.001$ on $256^3$ lattices). Acoustic radiation plus absence of free-streaming lowers the spherical-collapse threshold to an estimated $\delta_c\approx1.15$. The modified Press-Schechter cumulative halo density then yields a ${\sim}6\times$ enhancement at $z=10$ relative to $\Lambda$CDM:
\[
\frac{n_{\rm UHF}(>M)}{n_{\Lambda{\rm CDM}}(>M)}=\frac{\operatorname{erfc}(\delta_{\rm UHF}/\sqrt{2}\sigma)}{\operatorname{erfc}(\delta_{\rm GR}/\sqrt{2}\sigma)}\approx6.01
\]
(with $\sigma=0.71$), consistent in sign with excess early-galaxy counts reported by JWST.
Gross--Pitaevskii simulations of topological vortex halos show that defect anchoring stabilizes long-lived halo-like structures: a vortex halo retains $2.44\times$ more kinetic energy and $1.31\times$ more spatial structure ($\sigma^2$) than a defect-free clump evolving under identical conditions.
Macroscopic topological defects obey the Gauss linking integral $\operatorname{Lk}(\gamma_i,\gamma_j)\in\mathbb{Z}$, suggesting effectively collisionless propagation through baryonic plasma---a topological analogue of the $150\,\text{kpc}$ baryon--lensing offset in 1E 0657-558. Because mass requires defect seeds, the framework predicts strong suppression of baryon-free dark-matter subhalos, a falsifiable signature testable by Euclid, Roman, and LSST. All code and analysis scripts are publicly available.
\end{abstract}

\maketitle

\section{Introduction}
\label{sec:intro}

Standard $\Lambda$CDM requires collisionless particle dark matter to form halos and match large-scale structure. We explore whether the same superfluid condensate proposed in companion Letters as a model for emergent inertia and effective gravity could also address the JWST early-galaxy overabundance and the Bullet-Cluster offset, while offering a falsifiable prediction regarding baryon-free subhalos.

\section{Lowered Collapse Threshold and the JWST Anomaly}
\label{sec:jwst}

The condensate supplies an attractive Bjerknes acoustic force and eliminates collisionless velocity dispersion. Solving the spherical top-hat collapse equation with the additional acoustic term
\[
\ddot{\delta}+2H\dot{\delta}=4\pi G\rho_m\delta+\frac{4\pi G}{c_s^2}\langle\delta P_{\rm acoustic}\rangle
\]
yields $\delta_c^{\rm UHF}=1.15$. The Press-Schechter cumulative number density becomes
\[
n(>M,z)=\frac{\bar{\rho}}{M}\operatorname{erfc}\left(\frac{\delta_c^{\rm eff}(z)}{\sqrt{2}\,\sigma(M,z)}\right).
\]
At $z=10$ and $M=10^{10.5}M_\odot$ ($\sigma=0.71$), the ratio relative to $\Lambda$CDM ($\delta_c^{\rm GR}=1.686$) is exactly
\[
\frac{n_{\rm UHF}}{n_{\Lambda{\rm CDM}}}=\frac{\operatorname{erfc}(1.15/\sqrt{2}\cdot0.71)}{\operatorname{erfc}(1.686/\sqrt{2}\cdot0.71)}\approx6.01.
\]
At CMB epochs the condensate is elastic ($\omega_H\tau_M\gg1$), recovering standard peaks.

\section{Topological Collisionlessness and the Bullet Cluster}
\label{sec:bullet}

The gravitational lensing mass is carried by topological defects (quantized torus knots). These obey the Gauss linking integral
\[
\operatorname{Lk}(\gamma_i,\gamma_j)=\frac{1}{4\pi}\oint_{\gamma_i}\oint_{\gamma_j}\frac{(\mathbf{r}_i-\mathbf{r}_j)\cdot(d\mathbf{r}_i\times d\mathbf{r}_j)}{|\mathbf{r}_i-\mathbf{r}_j|^3}\in\mathbb{Z},
\]
an integer topological invariant conserved under smooth deformations. Defects therefore propagate collisionlessly through the baryonic plasma. The smooth condensate background contributes negligibly ($\delta\rho_0/\rho_0\lesssim10^{-4}$). Consequently the lensing map remains centered on the defect distribution, reproducing the observed $150\,\text{kpc}$ offset in 1E 0657-558 without fine-tuning.

\section{Heuristic Prediction: Baryon-Free Subhalo Suppression}
\label{sec:zero-subhalos}

If inertial mass requires non-zero local condensate density ($m=C\rho_0V$), then free-streaming or baryon-free clustering would be strongly suppressed. Defects would not form independently of baryonic seeds. The subhalo mass function for baryon-free objects would be negligible above the seeding scale ($\sim10^8$--$10^9M_\odot$). This prediction is falsifiable by Euclid, Roman, and LSST void-lensing stacking and subhalo counting: confirmed baryon-free subhalos or void-lensing excess $>3\sigma$ would rule out this scenario.

\section{Conclusion}
\label{sec:conclusion}

Topological defect anchoring stabilizes long-lived halo-like structures in UHF/GPE simulations, with vortex halos retaining $2.44\times$ more kinetic energy and $1.31\times$ more spatial structure than defect-free clumps. Combined with a lowered collapse threshold ($\delta_c\approx1.15$), these results suggest a heuristic scenario that is consistent in sign with the JWST early-galaxy excess and the Bullet-Cluster baryon--lensing offset. The predicted suppression of baryon-free subhalos is testable by forthcoming surveys. All results should be regarded as exploratory estimates within a simplified condensate model, not as replacements for $\Lambda$CDM.

\begin{acknowledgments}
Public verification code is available at \href{https://github.com/amiramitai/uhf}{github.com/amiramitai/uhf}. We thank the APS for consideration.
\end{acknowledgments}

\bibliography{references}

\end{document}
